---
title: "Lab 1: Scraping Web Pages"
author:
  - name: "Luke Romanik ^[Email: romanile@miamioh.edu]"
    affiliation: Farmer School of Business, Miami University
  - name: "Jacob Igel ^[Email: igeljj@miamioh.edu]"
    affiliation: Farmer School of Business, Miami University
  - name: "Jon Abaya ^[Email: abayajb@miamioh.edu]"
    affiliation: Farmer School of Business, Miami University
date: "Spring 2022"
output: 
  html_document:
    code_folding: show
    code_download: TRUE
    number_sections: TRUE
    paged_df: TRUE
    toc: TRUE
    toc_float: TRUE
    theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      progress = FALSE,
                      verbose = TRUE,
                      cache = TRUE)
```


---

# Required Packages
```{r packages}
# checking to see if the pacman package is installed + installing it if needed
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(rvest, tidyverse, magrittr, knitr, kableExtra)
```


---

# Scraping the Miami University Found and Impounded Property Listing

When you click on [Found and Impounded Property Listing](https://docs.google.com/spreadsheets/d/e/2PACX-1vQ3uk9AJOMODxS9fUgX_4vnEMj-Di7ulkTXWzPUmaHvHbaII63xmKmRu3VaBvOXrwQhtkOUlL9fxLMB/pubhtml?gid=1104208671&single=true) on the [Property - Lost, Found, Impounded Page](https://www.miamioh.edu/police/services/propertylostfoundimpounded/index.html), you will be taken to a Google Doc containing a table of lost and found items. 

**Please scrape the table and print it out.** Your code should be self-contained in the code chunk below.

```{r mu_lost_and_found}
mu_lost_found = read_html("https://docs.google.com/spreadsheets/d/e/2PACX-1vQ3uk9AJOMODxS9fUgX_4vnEMj-Di7ulkTXWzPUmaHvHbaII63xmKmRu3VaBvOXrwQhtkOUlL9fxLMB/pubhtml?gid=1104208671&single=true")

mu_lost_found = mu_lost_found %>% 
  html_element("table") %>%
  html_table(header = TRUE)
mu_lost_found = mu_lost_found[-c(0,2), -c(1)]
names(mu_lost_found) <- as.character(mu_lost_found[1,])
mu_lost_found <- mu_lost_found[-1,]
kable(mu_lost_found, caption = "MU Lost and Found") %>% kable_styling(fixed_thead = TRUE,bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


---

# Create a Table of all FSB Departmental Faculty/Staff

Currently, the Farmer School of Business has the following academic departments:
- [Accountancy](https://www.miamioh.edu/fsb/academics/accountancy/about/faculty-staff/index.html)  
- [Economics](https://www.miamioh.edu/fsb/academics/economics/about/faculty-staff/index.html) 
- [Entrepreneurship](https://www.miamioh.edu/fsb/academics/entrepreneurship/about/faculty-staff/index.html)  
- [Finance](https://www.miamioh.edu/fsb/academics/finance/about/faculty-staff/index.html)
- [Information Systems & Analytics](https://www.miamioh.edu/fsb/academics/isa/about/faculty-staff/index.html)  
- [Marketing](https://www.miamioh.edu/fsb/academics/marketing/about/faculty-staff/index.html)  
- [Management](https://www.miamioh.edu/fsb/academics/management/about/faculty-staff/index.html)  

Using the code chunk below, please write code that will produce and print a **single tibble containing information on ALL departments and the following variables:** (a) department name, (b) faculty/staff's name, (c) faculty/staff's position, and (d) faculty/staff's website

```{r fsb_faculty_staff}
vector_of_urls = list("https://www.miamioh.edu/fsb/academics/accountancy/about/faculty-staff/index.html",
                      "https://www.miamioh.edu/fsb/academics/economics/about/faculty-staff/index.html",
                      "https://www.miamioh.edu/fsb/academics/entrepreneurship/about/faculty-staff/index.html",
                      "https://www.miamioh.edu/fsb/academics/finance/about/faculty-staff/index.html",
                      "https://www.miamioh.edu/fsb/academics/isa/about/faculty-staff/index.html",
                      "https://www.miamioh.edu/fsb/academics/marketing/about/faculty-staff/index.html",
                      "https://www.miamioh.edu/fsb/academics/management/about/faculty-staff/index.html")

scrape_fsb_faculty = function(url){
  fac_url = read_html(url)
  temp <- set_names(data.frame(cbind(
    html_text2(html_nodes(fac_url, 'tr > td'))[seq(from = 1, to = length( html_text2(html_nodes(fac_url, 'tr > td'))), by = 3)],
    html_text2(html_nodes(fac_url, 'tr> td> strong > a')),
    html_text2(html_nodes(fac_url, 'tr > td > i')) %>% 
      str_replace_all(.,"\\n", " ") %>% 
      str_trim(., side = c("both")),
    html_nodes(fac_url,'a') %>% 
      html_attr('href') %>% 
      str_subset(., "http://miamioh.edu/fsb/directory")
  )), c('Department Name', 'Faculty Name', 'Faculty Position', 'Faculty Website'))
  return(temp)
}

all_fsb_faculty = map_df(.x = vector_of_urls, .f = scrape_fsb_faculty)
all_fsb_faculty = as_tibble(all_fsb_faculty)
kable(all_fsb_faculty, caption = "FSB faculty") %>% kable_styling(fixed_thead = TRUE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


---

# Netflix Ratings on IMDb

The most popular listings on Netflix are rated and reviews on [ImDb](https://www.imdb.com/search/title/?companies=co0144901). Based on this webpage and its following pages, please create a **tibble** that contains the following:

- *Title:*  
- *Years:*
- *Age classification:*
- *Duration:*
- *Genres:*
- *IMDb Rating:*
- *1-2 Sentence Summary:*
- *Stars:*
- *Votes:*

**Your tibble should contain a variable for the 9 items above for each of the 50 titles found on the page.** 

```{r netflix_imdb_p1}

scrape_test_imbd <- function(url){
  yo = tibble()
  temp = read_html(url)
  sections <- html_nodes(temp, '#main > div > div.lister.list.detail.sub-list > div > div > div.lister-item-content')
  for (s in sections) {
    title = html_text2(html_nodes(s, 'h3 > a'))
    year = html_text2(html_nodes(s, 'h3 > span.lister-item-year.text-muted.unbold')) %>% 
      gsub('[A-Za-z()" "]*','', .)
    if(year == ""){
      year = 'NULL'
    }
    else if((substr(year,(nchar(year)+1)-1,nchar(year))) == "–"){
      year = paste(year, "present", sep = "")
    }
    genre = html_text2(html_nodes(s, 'p > span.genre'))
    paras <- length(html_nodes(s, 'p'))
    info_spans <- length(html_nodes(s, 'p:nth-child(2) > span'))
    if(paras == 3 & info_spans != 5){
      if(title == "The Adam Project"){
        age_class = 'NULL'
        duration = html_text2(html_nodes(s, 'p > span.runtime'))
        rating = 'NULL'
        summary = html_text2(html_nodes(s, 'p:nth-child(3)'))
        stars = html_text2(html_nodes(s, 'p:nth-child(4)'))
        votes = 'NULL'
      } else if(title == "That '90s Show"){
          age_class = html_text2(html_nodes(s, 'p > span.certificate'))
          duration = html_text2(html_nodes(s, 'p > span.runtime'))
          rating = 'NULL'
          summary = html_text2(html_nodes(s, 'p:nth-child(3)'))
          stars = html_text2(html_nodes(s, 'p:nth-child(4)'))
          votes = 'NULL'
      } else if(info_spans == 2){
        age_class = 'NULL'
        duration = 'NULL'
        rating = 'NULL'
        summary = html_text2(html_nodes(s, 'p:nth-child(3)'))
        stars = html_text2(html_nodes(s, 'p:nth-child(4)'))
        votes = 'NULL'
      } else if(info_spans == 4){
        age_class = html_text2(html_nodes(s, 'p > span.certificate'))
        duration = 'NULL'
        rating = 'NULL'
        summary = html_text2(html_nodes(s, 'p:nth-child(3)'))
        stars = html_text2(html_nodes(s, 'p:nth-child(4)'))
        votes = 'NULL'
      } else if(info_spans == 6){
        age_class = html_text2(html_nodes(s, 'p > span.certificate'))
        duration = html_text2(html_nodes(s, 'p > span.runtime'))
        rating = 'NULL'
        summary = html_text2(html_nodes(s, 'p:nth-child(3)'))
        stars = html_text2(html_nodes(s, 'p:nth-child(4)'))
        votes = 'NULL'
      }else{
        age_class = 'NULL'
        duration = 'NULL'
        rating = 'NULL'
        summary = 'NULL'
        stars = 'NULL'
        votes = 'NULL'
      }
      
    }else if(paras == 4 & info_spans != 5){
      if(title == "Bulgasal" | title == "Our Beloved Summer"){
        age_class = 'NULL'
        duration = html_text2(html_nodes(s, 'p > span.runtime'))
        rating = html_text2(html_nodes(s, 'div > div.inline-block.ratings-imdb-rating > strong'))
        summary = html_text2(html_nodes(s, 'p:nth-child(4)'))
        stars = html_text2(html_nodes(s, 'p:nth-child(5)'))
        votes = html_text2(html_nodes(s, 'p.sort-num_votes-visible > span:nth-child(2)'))
      } else if(title == "Toy Boy"){
          age_class = html_text2(html_nodes(s, 'p > span.certificate'))
          duration = 'NULL'
          rating = html_text2(html_nodes(s, 'div > div.inline-block.ratings-imdb-rating > strong'))
          summary = html_text2(html_nodes(s, 'p:nth-child(4)'))
          stars = html_text2(html_nodes(s, 'p:nth-child(5)'))
          votes = html_text2(html_nodes(s, 'p.sort-num_votes-visible > span:nth-child(2)'))
      }
      else if(info_spans == 6){
          age_class = html_text2(html_nodes(s, 'p > span.certificate'))
          duration = html_text2(html_nodes(s, 'p > span.runtime'))
          rating = html_text2(html_nodes(s, 'div > div.inline-block.ratings-imdb-rating > strong'))
          summary = html_text2(html_nodes(s, 'p:nth-child(4)'))
          stars = html_text2(html_nodes(s, 'p:nth-child(5)'))
          votes = html_text2(html_nodes(s, 'p.sort-num_votes-visible > span:nth-child(2)'))
      } else if(info_spans == 3){
          age_class = html_text2(html_nodes(s, 'p > span.certificate'))
          duration = 'NULL'
          rating = html_text2(html_nodes(s, 'div > div.inline-block.ratings-imdb-rating > strong'))
          summary = html_text2(html_nodes(s, 'p:nth-child(4)'))
          stars = html_text2(html_nodes(s, 'p:nth-child(5)'))
          votes = html_text2(html_nodes(s, 'p.sort-num_votes-visible > span:nth-child(2)'))
      }else{
        age_class = 'NULL'
        duration = 'NULL'
        rating = 'NULL'
        summary = 'NULL'
        stars = 'NULL'
        votes = 'NULL'
      }
    }
    else{
      age_class = html_text2(html_nodes(s, 'p > span.certificate'))
      duration = html_text2(html_nodes(s, 'p > span.runtime'))
      rating = html_text2(html_nodes(s, 'div > div.inline-block.ratings-imdb-rating > strong'))
      summary = html_text2(html_nodes(s, 'p:nth-child(4)'))
      stars = html_text2(html_nodes(s, 'p:nth-child(5)'))
      votes = html_text2(html_nodes(s, 'p.sort-num_votes-visible > span:nth-child(2)'))
    }
    yo = rbind(yo, data.frame(title, year, age_class, duration, genre, rating, summary, stars, votes))
  }
  return(yo)
}
netflix_top_50 = scrape_test_imbd("https://www.imdb.com/search/title/?companies=co0144901")
kable(netflix_top_50, caption = "Netflix Top 50") %>% kable_styling(fixed_thead = TRUE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

---

# Top 300 Netflix Ratings 

Expand on the previous example to capture the top **300** titles on Netflix (i.e., the information across six pages).

```{r netflix_imdb_p2}
test_scrape_300 = tibble()
base_url = 'https://www.imdb.com/search/title/?companies=co0144901'
start = 0
count = 1
while (start <= 251) {
  intrest_url = paste0(base_url,"&start=",start,"&ref_=adv_nxt")
  test_scrape_300 = rbind(test_scrape_300, scrape_test_imbd(intrest_url))
  start = (start + 50) + count
  count = 0
}
kable(test_scrape_300, caption = "Netflix Top 300") %>% kable_styling(fixed_thead = TRUE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


---

# Yelp Reviews for Patterson Cafe
In assignment 02, I shared with you an RDS file containing four variables and all the reviews that were performed on [Patterson Cafe on Yelp](https://www.yelp.com/biz/pattersons-cafe-oxford). Use what you have learned in class to potentially recreate the same results.

```{r yelp_reviews}
base_url = 'https://www.yelp.com/biz/pattersons-cafe-oxford'
start = 0
yelp_reviews = tibble()

scrape_yelp <- function(url){
  temp = read_html(url)
  df <- set_names(data.frame(cbind(
    html_text2(html_nodes(temp, 'div.user-passport-info.border-color--default__09f24__NPAKY > span > a')),
    html_text2(html_nodes(temp, 'div > ul > li> div > div.margin-t1__09f24__w96jn.margin-b1-5__09f24__NHcQi.border-color--default__09f24__NPAKY > div > div.arrange-unit__09f24__rqHTg.arrange-unit-fill__09f24__CUubG.border-color--default__09f24__NPAKY > span.css-1e4fdj9')),
    html_nodes(temp, 'div.css-79elbk.border-color--default__09f24__NPAKY > div > ul > li > div > div.margin-t1__09f24__w96jn.margin-b1-5__09f24__NHcQi.border-color--default__09f24__NPAKY > div > div:nth-child(1) > span > div') %>% 
      html_attr("aria-label") %>% 
      substr(., 1, 1),
    html_text2(html_nodes(temp, 'div > div.margin-b2__09f24__CEMjT.border-color--default__09f24__NPAKY > p > span'))
  )), c('reviewer', 'review_date', 'score', 'comment'))
  return(df)
}

while (start <= 90) {
  intrest_url = paste0(base_url, "?start=", start)
  yelp_reviews = rbind(yelp_reviews, scrape_yelp(intrest_url))
  start = start + 10
}

kable(yelp_reviews, caption = "Patterson Cafe Reviews") %>% kable_styling(fixed_thead = TRUE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

